---
title       : Developing Data Product- Final Project
subtitle    : MPG Predictor
author      : Jeff Fan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The background of MPG Predictor

Background: It is just a simple implementation for shinyApp. I run the regression model 
based on the mtcars dataset in R. And using the model to predict user's car mpg.Just a simple app:)
Dependency:
```{r, results='hide'}
library(shiny)
library(MASS)
library(datasets)
data(mtcars)
```
--- .class #id 
## How we get the model?
First, we should using all the variables in this dataset to make a regression model,
Then we gonna to using stepwise algorithm for this dataset to narrow down the primary factors for mpg,
```{r, results='hide'}
model_all <- glm(mpg ~ as.factor(gear) + as.factor(carb) + as.factor(vs) + as.factor(cyl)+as.factor(am)+ disp + hp + drat + wt + qsec, data = mtcars)
stepwise_regression <- stepAIC(model_all, direction = "both")

```
--- .class #id 
## The final model
The final model and estimate intercepet is shown below,
```{r}
stepwise_regression$coefficients
final <- glm(mpg ~  as.factor(cyl) + as.factor(am) + hp + wt, data = mtcars)
```
--- .class #id 
## Try yourself!
Input your car's information and clicked the "Submit" button, you could see the mpg is shown!

